### 2020-07-05 README.Rmd
[docs] Update build badge in README [skip-ci]

<!-- badges: start -->
[![R build status](https://github.com/ideas-lab-nus/eplusr-paper/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/eplusr-paper/actions)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R build status](https://github.com/ideas-lab-nus/eplusr-paper/workflows/eplusr-paper/badge.svg)](https://github.com/ideas-lab-nus/eplusr-paper/actions)
<!-- badges: end -->
